### 2013-10-09 src2/thesis.tex
apa

\subsection*{GPU Programming papers}

@@

Computers today are increasingly parallel. With each new generation of 
general purpose processor or GPU we get more parallel resources. To 
fully make use of modern CPUs and GPUs we need to fully exploit their 
parallelism.

Modern CPUs are parallel in a number of different ways. They discover instruction
level parallelism(ILP), they have multiple processor cores and vector units for 
Single Instruction Multiple Data parallelism. The exact configurations, number
of cores and number of vector units, vary over available processors.

@@

\section{An embedded languages approach to data-parallelism}

@@

@@

\chapter{EDSL implementation papers}
\label{chap:EDSLImplementation}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

@@

\chapter{GPU programming papers}
\label{chap:GPUProgramming}

@@

\chapter{Retargetable parallel programming papers}
\label{chap:ArBB}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

>>>>

\subsection*{GPU programming papers}

@@

This thesis is about applying embedded language techniques to programming 
multi- and many-core computers. Computers today are becoming more and more  
parallel. With each new generation of 
general purpose processor (CPU) or graphics processor (GPU) we get more 
parallel resources. To fully make use of modern CPUs and GPUs we need to fully 
exploit their parallelism.

Modern CPUs are parallel in a number of different ways. They discover instruction
level parallelism (ILP), they have multiple processor cores and vector units for 
Single Instruction Multiple Data parallelism. The exact configuration, number
of cores and number of vector units, vary over available processor models. 
To obtain maximum performance, with a specific target processor in mind, the programmer
would use low-level intrinsics in order to get SIMD parallelism and some threading library
for parallelism over the available cores. One problem with this is that the resulting program 
would be specialised to a specific processor model.

In chapter~\ref{chap:ArBB},

@@

\section{Embedded languages}

\section{Obsidian: An embedded language for GPU kernel implementation}

@@

\section{Embedding Intel Array Building Blocks}

\noindent\emph{Short section about the approach taken with EmbArBB}

@@

\chapter{EDSL Implementation Papers}
\label{chap:EDSLImplementation}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

@@

\chapter{GPU Programming Papers}
\label{chap:GPUProgramming}

@@

\chapter{Retargetable Parallel Programming Papers}
\label{chap:ArBB}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage
